---
title: "Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
This dataset gives information about the largest online store in Brazil - 'Olist'. Small businesses can use the platform to sell their products on the side and ship them by using the Olist logistic partners.\
The dataset contains (pseudo-) anonymised data of orders from 2016 to 2018.\



Importing the libraries
```{r, echo = FALSE}
library(ggplot2)
library(dplyr)
library(forcats)
library(tidyverse)
```

Reading the CSVs
```{r}
customers <- read.csv("C:\\Users\\nikla\\Documents\\Uni\\Semester_3\\DASC\\Datasets\\BrazilianEcommerce\\olist_customers_dataset.csv")
orders <- read.csv("C:\\Users\\nikla\\Documents\\Uni\\Semester_3\\DASC\\Datasets\\BrazilianEcommerce\\olist_orders_dataset.csv")
order_items <- read.csv("C:\\Users\\nikla\\Documents\\Uni\\Semester_3\\DASC\\Datasets\\BrazilianEcommerce\\olist_order_items_dataset.csv")
state_information <-read.csv("C:\\Users\\nikla\\Documents\\Uni\\Semester_3\\DASC\\Datasets\\BrazilianEcommerce\\brazil_state_information.csv", sep = ";")
```



Joining the tables together
```{r}
orders_customer_items <- orders %>%
  left_join(customers, "customer_id") %>%
  left_join(order_items, "order_id")
```


We want to focus the data analysis on one business year, therefore the data is filtered to only contain orders which have been approved in 2017
```{r}
orders_customer_items <- orders_customer_items %>%
  filter(startsWith(order_approved_at, "2017"))
head(orders_customer_items, n=10)
```


In this code chunk, we create a new table which contains the average price per order for each state.
Therefore we have to calculate the total order price first and after that we can group by the customer state and calculate the average.
```{r}
avg_order_item_price_by_state <- orders_customer_items %>%
  group_by(order_id) %>%
  summarise(
    order_price = sum(price),
    customer_state = customer_state
  ) %>%
  group_by(customer_state) %>%
  summarise(
    avg_price = round(mean(order_price, na.rm = TRUE), digits = 2)
  )
avg_order_item_price_by_state
```

In this plot you can see the average price per order or each state. 
```{r}
 ggplot(data = avg_order_item_price_by_state, aes(fct_reorder(customer_state, avg_price), avg_price)) +
  geom_col(fill = "#FF6666") +
  ggtitle("Average price of one order per state") +
  xlab("State") + ylab("Average price per order in R$") +
  theme(
    plot.title = element_text(hjust = 0.5),
)
```

In the next step we want to take a look at the total revenue by each state. Afterwards we can compare it with the average price per order.
```{r}
revenue_by_state <- orders_customer_items %>%
  group_by(customer_state) %>%
  summarise(
    revenue = sum(price, na.rm = TRUE)
  )
revenue_by_state

 ggplot(data = revenue_by_state, aes(fct_reorder(customer_state, revenue), revenue)) +
  geom_col(fill = "#FF6666") +
  ggtitle("Total revenue per state") +
  xlab("State") + ylab("Revenue in R$") +
  theme(
    plot.title = element_text(hjust = 0.5),
)
```

This plot shows the pure amount of orders for each state.
```{r}
order_count_by_state <- orders_customer_items %>%
  group_by(customer_state) %>%
  summarise(
    amountOfOrders = n()
  )

 ggplot(data = order_count_by_state, aes(fct_reorder(customer_state, amountOfOrders), amountOfOrders)) +
  geom_col(fill = "#FF6666") +
  ggtitle("Number of orders per state") +
  xlab("State") + ylab("Amount of orders") +
  theme(
    plot.title = element_text(hjust = 0.5),
)
```
Comparing the 3 plots, we can see that São Paulo definetly makes 


# Notes
- Sales per state
- Monthly sales/revenue
- Maybe search a data set which gives info about the economic performance of each state


