---
title: "Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
This dataset gives information about the largest online store in Brazil - 'Olist'. Small businesses can use the platform to sell their products on the side and ship them by using the Olist logistic partners.\
The dataset contains (pseudo-) anonymised data of orders from 2016 to 2018.\



Importing the libraries
```{r, echo = FALSE}
library(ggplot2)
library(dplyr)
library(forcats)
library(tidyverse)
```

Reading the CSVs
```{r}
customers <- read.csv("C:\\Users\\nikla\\Documents\\Uni\\Semester_3\\DASC\\Datasets\\BrazilianEcommerce\\olist_customers_dataset.csv")
orders <- read.csv("C:\\Users\\nikla\\Documents\\Uni\\Semester_3\\DASC\\Datasets\\BrazilianEcommerce\\olist_orders_dataset.csv")
order_items <- read.csv("C:\\Users\\nikla\\Documents\\Uni\\Semester_3\\DASC\\Datasets\\BrazilianEcommerce\\olist_order_items_dataset.csv")
state_information <-read.csv("C:\\Users\\nikla\\Documents\\Uni\\Semester_3\\DASC\\Datasets\\BrazilianEcommerce\\brazil_state_information.csv", sep = ";")
```



Joining the tables together
```{r}
orders_customer_items <- orders %>%
  left_join(customers, "customer_id") %>%
  left_join(order_items, "order_id")
```


We want to focus the data analysis on one business year, therefore the data is filtered to only contain orders which have been approved in 2017. The data now contains orders from 2017-01-05 to 2017-12-31.
```{r}
orders_customer_items <- transform(orders_customer_items, order_approved_at = as.Date(order_approved_at, format = "%Y-%m-%d"))
orders_customer_items <- orders_customer_items %>%
  filter(format(order_approved_at, "%Y") == "2017")
orders_customer_items$month <- as.numeric(format(orders_customer_items$order_approved_at, "%m"))
head(orders_customer_items, n=5)
```
## Comparing the different states

The next plots show the amount of orders per state from 2017 and the total revenue made by each state in 2017
```{r}
order_info_by_state <- orders_customer_items %>%
  group_by(customer_state) %>%
  summarise(
    amountOfOrders = n(),
    revenue = sum(price, na.rm = TRUE)
  )

#Order count plot
 ggplot(data = order_info_by_state, aes(fct_reorder(customer_state, amountOfOrders), amountOfOrders)) +
  geom_col(fill = "#FF6666") +
  ggtitle("Number of orders per state") +
  xlab("State") + ylab("Amount of orders") +
  theme(
    plot.title = element_text(hjust = 0.5),
)
 
#Revenue plot
 ggplot(data = order_info_by_state, aes(fct_reorder(customer_state, revenue), revenue)) +
  geom_col(fill = "#FF6666") +
  ggtitle("Total revenue per state") +
  xlab("State") + ylab("Revenue in R$") +
  theme(
    plot.title = element_text(hjust = 0.5),
)
 
```

You can see that these variables seem to correlate. Which is clear regarding the fact that more orders bring a larger. 
It is clearly visible as well that SP (São Paulo) is the most important state of brazil in terms of economy.

```{r}
#Both plots normalized
# order_info_by_state %>%
#   transform(revenue = (revenue-min(revenue))/(max(revenue)-min(revenue)), 
#             amountOfOrders = (amountOfOrders-min(amountOfOrders))/(max(amountOfOrders)-min(amountOfOrders))) %>%
#   tidyr::pivot_longer(cols=c('amountOfOrders', 'revenue'), names_to='variable', values_to="value") %>%
#   ggplot(aes(x=fct_reorder(customer_state, value), y=value, fill=variable)) +
#   geom_col(position = "dodge") +
#   ggtitle("Amount of orders and the revenue compared for each state") +
#   xlab("State") + ylab("Normalized values")

order_info_by_state$amountOfOrders_scaled <- scale(order_info_by_state$amountOfOrders, center = FALSE, scale = TRUE)
order_info_by_state$revenue_scaled <- scale(order_info_by_state$revenue, center = FALSE, scale = TRUE)

order_info_by_state %>%
  tidyr::pivot_longer(cols=c('amountOfOrders_scaled', 'revenue_scaled'), names_to='variable', values_to="value") %>%
  ggplot(aes(x=fct_reorder(customer_state, value), y=value, fill=variable)) +
  geom_col(position = "dodge") +
  ggtitle("Amount of orders and the revenue compared for each state") +
  xlab("State") + ylab("Normalized values")

```



In this code chunk, we create a new table which contains the average price per order for each state.
Therefore we have to calculate the total order price first and after that we can group by the customer state and calculate the average.
```{r}
avg_order_item_price_by_state <- orders_customer_items %>%
  group_by(order_id) %>%
  summarise(
    order_price = sum(price),
    customer_state = customer_state
  ) %>%
  group_by(customer_state) %>%
  summarise(
    avg_price = round(mean(order_price, na.rm = TRUE), digits = 2)
  )
avg_order_item_price_by_state
```

In this plot you can see the average price per order or each state. 
```{r}
 ggplot(data = avg_order_item_price_by_state, aes(fct_reorder(customer_state, avg_price), avg_price)) +
  geom_col(fill = "#FF6666") +
  ggtitle("Average price of one order per state") +
  xlab("State") + ylab("Average price per order in R$") +
  theme(
    plot.title = element_text(hjust = 0.5),
)
```

In the next step we want to take a look at the total revenue by each state. Afterwards we can compare it with the average price per order.
```{r}
revenue_by_state <- orders_customer_items %>%
  group_by(customer_state) %>%
  summarise(
    revenue = sum(price, na.rm = TRUE)
  )
 ggplot(data = revenue_by_state, aes(fct_reorder(customer_state, revenue), revenue)) +
  geom_col(fill = "#FF6666") +
  ggtitle("Total revenue per state") +
  xlab("State") + ylab("Revenue in R$") +
  theme(
    plot.title = element_text(hjust = 0.5),
)
```



Comparing the 3 plots, we can see that São Paulo definitely makes the most revenue. Which is not really surprising regarding the fact it is Brazil's most populous city.  

Average amount of money one customer spends per state
```{r}
avg_money_spent <- orders_customer_items %>%
  group_by(customer_id) %>%
  summarise(
    money_spent = sum(price),
    customer_state = customer_state
  ) %>%
  group_by(customer_state) %>%
  summarise(
    avg = round(mean(money_spent, na.rm = TRUE), digits = 2)
  )

 ggplot(data = avg_money_spent, aes(fct_reorder(customer_state, avg), avg)) +
  geom_col(fill = "#FF6666") +
  ggtitle("Average money spent by one customer per state") +
  xlab("State") + ylab("Average money spent in 2017 in R$") +
  theme(
    plot.title = element_text(hjust = 0.5),
)
 
orders_customer_items %>%
  group_by(customer_id) %>%
  summarise(
    money_spent = sum(price),
    customer_state = customer_state
  ) %>%
  filter (customer_state %in% c("SP", "RJ", "MG", "RS")) %>%
  filter (money_spent < 1000) %>%
  left_join(state_information, c("customer_state" = "abbreviation")) %>%
  ggplot(mapping = aes(x = state, y = money_spent)) +
  geom_boxplot(mapping = aes(color = state)) +
  ggtitle("Money spent by one customer per state") +
  xlab("State") + ylab("Money spent in 2017 in R$") +
  theme (
    plot.title = element_text(hjust = 0.5),
  )


# orders_customer_items %>%
#   group_by(customer_id) %>%
#   summarise(
#     money_spent = sum(price),
#     customer_state = customer_state
#   ) %>%
#   filter (customer_state %in% c("SP", "RJ", "MG", "RS")) %>%
#   filter (money_spent < 1000) %>%
#   ggplot(mapping = aes(x = customer_state, y = money_spent, fill = customer_state)) +
#   geom_violin()
 
```

## Revenue per month
```{r}
revenue_by_month <- orders_customer_items %>%
  group_by(month) %>%
  summarise(
    revenue_by_month = sum(price, na.rm = TRUE)
  ) 
ggplot(data = revenue_by_month, aes(x = month, y = revenue_by_month)) +
  geom_point(size=4, color = "#FF6666") +
  geom_line(size = 1, color = "#FF6666") +
  ggtitle("Monthly Revenue") +
  xlab("Month (2017)") + ylab("Revenue in R$") +
  theme(
    plot.title = element_text(hjust = 0.5),
) +
  geom_smooth(method =lm, level=0.95)

```



#Regression (Niklas)
```{r}
snens <- avg_money_spent %>%
  left_join(state_information, c("customer_state" = "abbreviation"))
snens$pop_per_sq_km <- (snens$population / snens$size)
snens
frist_regression <- lm(avg ~ gnp, data = snens)
summary(frist_regression)
plot (snens$pop_per_sq_km, snens$avg)
#summary(lm(avg ~ gnp + population, data = snens))

```

```{r}
revnue_state_info <- revenue_by_state %>%
  left_join(state_information, c("customer_state" = "abbreviation"))
revnue_state_info$pop_per_sq_km <- (revnue_state_info$population / revnue_state_info$size)
#revnue_state_info <- revnue_state_info %>%
 # filter(!(customer_state %in% c( "RR", "AP", "AC")))
revnue_state_info <- revnue_state_info %>%
  filter(!(customer_state %in% c( "SP")))

revenue_pop_regression <- lm(revenue ~ population, data = revnue_state_info)
summary(revenue_pop_regression)

ggplot(data = revnue_state_info, aes(x=population, y=revenue)) + geom_point() + geom_smooth(method =lm, level=0.95)
par(mfrow=c(2,2))
plot (revenue_pop_regression)
```
Good stuff
- Normal Q-Q (Residuals are normally distributed)
- Scale-Location is quite okay, variance is spread equally

Bad stuff:
- Residuals vs Fitted is not really a straight line but it's okay (Residuals are a bit far away sometimes (26 - SP not fitting))


# Monthly revenue regression
```{r}
monthly_revenue_reg <- lm(revenue_by_month ~ month, data = revenue_by_month)
  
summary(monthly_revenue_reg)
par(mfrow=c(2,2))
plot(monthly_revenue_reg)

print("-----------!!!!!!!!!!!!-----------")
monthly_revenue_reg <- lm(revenue_by_month ~ month, data = revenue_by_month[-c(11), ])
  
summary(monthly_revenue_reg)
par(mfrow=c(2,2))
plot(monthly_revenue_reg)
```


# Notes
- Compare avg. ppo with avg money spend by customers in one year
- Sales per state
- Monthly sales/revenue
- Maybe search a data set which gives info about the economic performance of each state


